---
title: "Corpus: Chats"
execute: 
  eval: false
editor_options: 
  chunk_output_type: console
---

::: callout-note
## Information

Based on the **chat** data, this script:
-   Creates a corpus, tokens, and a document-feature matrix with the `quanteda` package [`r glue::glue("v{packageVersion('quanteda')}")`, @benoit2018].
-   Utilizes `udpipe` [`r glue::glue("v{packageVersion('udpipe')}")`, @wijffels2023] and `spacyr` [`r glue::glue("v{packageVersion('spacyr')}")`, @benoit2023] packages for additional linguistic processing, adding lemmatization, part-of-speech tagging, and named entity recognition.

:::

## Preparation

```{r setup-session}
#| warning: false
#| message: false

# Load packages
source(file = here::here(
  "data_collection/00_02-setup-session.R"
))
```

```{r data-import}

chat <- qs::qread(here("local_data/chat-debates_full.qs"))
chat_corpora <- qs::qread(here("local_data/chat-corpora_full.qs"))
```

## Process data

```{r create-corpus}
chat_corpora <- list()

# Create corpus
chat_corpora$corp <- chat$hashed %>% 
    quanteda::corpus(
        docid_field = "message_id", 
        text_field = "message_content"
  )

# Create tokens
chat_corpora$toks <- chat_corpora$corp %>% 
    quanteda::tokens() 

# Create Document Feature Matrix (DFM)
chat_corpora$dfm <- chat_corpora$toks %>% 
    quanteda::dfm()
```


```{r create-udpipe}
# Execute on first run, to download the model 
# udmodel <- udpipe::udpipe_download_model(
#     language = "english",
#     model_dir = here("models"))

# Load udpipe model
udmodel_english <- udpipe::udpipe_load_model(file = here("models/english-ewt-ud-2.5-191206.udpipe"))

chat_corpora$udpipe <- chat$hashed %>% 
  rename(
    doc_id = message_id,
    text = message_content
  ) %>% 
  udpipe::udpipe(udmodel_english)
```


```{r create-spacyr}
# Define environment
reticulate::use_virtualenv("r-spacyr")

# Initialize
spacyr::spacy_download_langmodel("en_core_web_sm")
spacyr::spacy_initialize("en_core_web_sm")

chat_corpora$spacyr <- chat_corpora$corp %>% 
    spacyr::spacy_parse(.,
        tag = TRUE,
        pos = TRUE,
        lemma = TRUE,
        dependency = TRUE,
        multithread = TRUE
    )
```

## Save data
```{r}
# Save complete data
qs::qsave(
    chat_corpora,
    file = here("local_data/chat-corpora_full.qs")
)

# Save udpipe corpus
qs::qsave(
    chat_corpora$udpipe, 
    file = here("local_data/chat-corpus_udpipe.qs")
)

# Save spacyr corpus
qs::qsave(
    chat_corpora$spacyr, 
    file = here("local_data/chat-corpus_spacyr.qs")
)
```
