---
title: "Quality Control: Chat Badges"
editor_options: 
  chunk_output_type: console
---

::: callout-tip
## Information
- The document sets up the session by sourcing a setup script.
- It imports chat data from a local file.
- It creates a list of user badges from the chat data.
- It provides a link to example images of the badges.
- It analyzes the frequency and distribution of badges per message.
:::

## Preparation

```{r setup-session}
#| warning: false
#| message: false

source(here::here("data_collection/00_02-setup-session.R"))
```

```{r import-data}
# Load data
chat <- qs::qread(here("local_data/chat-debates_full.qs"))
```

## Create list of badges

```{r data-badges-creation}
badges <- chat$correct %>%
    select(message_id, user_badges) %>%
    unnest(user_badges) %>%
    mutate(
        badge_name = sapply(user_badges, function(badge) badge$name),
    ) %>%
    unnest(badge_name)
```

::: callout-note
For example images of the emojis visit https://twitchinsights.net/badges
:::

```{r}
badges %>% 
    frq(badge_name)
```

## Distribution of badges per message

```{r}
badges %>% 
    group_by(message_id) %>% 
    summarise( n = n()) %>% 
    describe_distribution()
```
