---
title: "🔨 Sentiment Analysis with R"
subtitle: "Tutorial - Session 10"
date: last-modified
date-format: "DD.MM.YYYY"
---

::: {.callout-tip icon="false"}
[![Quarto Slides](https://raw.githubusercontent.com/faucommsci/teaching_materials/refs/heads/main/images/badges/badge-quarto-slide.svg) Link to slides](../slides/slides-10.html)

[![](https://raw.githubusercontent.com/faucommsci/teaching_materials/refs/heads/main/images/badges/badge-quarto_document.svg) Download source file](https://github.com/chrdrn/dbd_2024/blob/main/tutorials/tutorial-10.qmd)

[![](https://raw.githubusercontent.com/faucommsci/teaching_materials/refs/heads/main/images/badges/badge-binder_rstudio.svg) Open interactive and executable RStudio environment](https://mybinder.org/v2/gh/faucommsci/dbd_binder/HEAD?urlpath=rstudio)
:::

## Background

## Preparation

```{r load-packages}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
    here, 
    magrittr, janitor,
    ggpubr, ggdist, ggsci,
    gt, gtExtras,
    countdown, 
    quanteda, # quanteda text processing
    quanteda.textplots, quanteda.textstats, 
    quanteda.textmodels, quanteda.sentiment, 
    ellmer, rollama,
    tidymodels,
    easystats, tidyverse
)
```

```{r import-data-frontend}
#| eval: false
# Import base data
chats <- qs::qread(here("local_data/chats.qs"))
corp_chats <- chats %>% 
    quanteda::corpus(docid_field = "message_id", text_field = "message_content")
```

```{r import-data-backend}
#| echo: false
chats <- qs::qread(here("local_data/chats.qs"))
chats_polarity <- qs::qread(here("local_data/chats-sentiment_polarity.qs"))
chats_valence <- qs::qread(here("local_data/chats-sentiment_valence.qs"))
chats_vader <- qs::qread(here("local_data/chats-sentiment_vader.qs"))
chats_sentiment <- chats %>% 
    left_join(chats_polarity, by = join_by("message_id" == "doc_id")) %>%
    left_join(chats_valence, by = join_by("message_id" == "doc_id")) %>% 
    left_join(chats_vader %>% 
        select(message_id, vader_output, word_scores, compound, pos, neu, neg, but_count), 
        by = "message_id")
lasso_grid <- qs::qread(here("local_data/tidymodels-lasso_grid.qs"))
```

## Codechunks aus der Sitzung

### Praktische Anwedung von `quanteda.sentiment`

```{r chats-polarity-create}
#| eval: false
chats_polarity <- corp_chats %>% 
  textstat_polarity(
    dictionary = data_dictionary_LSD2015) %>% 
  rename(polarity = sentiment)
```

```{r chats-polarity-output}
chats_polarity %>% 
    head(n = 10) 
```

```{r chats-valence-create}
#| eval: false
chats_valence <- corp_chats %>% 
  textstat_valence(
    dictionary = data_dictionary_AFINN) %>% 
  rename(valence = sentiment)
```

```{r chats-valence-output}
chats_valence %>% 
    head(n = 10)
```

```{r save-sentiment-data-backend}
#| eval: false
#| echo: false

qs::qsave(chats_polarity, file = here("local_data/chats-sentiment_polarity.qs"))
qs::qsave(chats_valence, file = here("local_data/chats-sentiment_valence.qs"))
```

### Praktische Anwedung von `vader`

```{r vader-data-create}
#| eval: false

chats_vader <- chats %>% 
  mutate(
    vader_output = map(message_content, ~vader::get_vader(.x)), 
    # Extract word-level scores
    word_scores = map(vader_output, ~ .x[
        names(.x) != "compound" &
        names(.x) != "pos" & 
        names(.x) != "neu" & 
        names(.x) != "neg" & 
        names(.x) != "but_count"]),  
    compound = map_dbl(vader_output, ~ as.numeric(.x["compound"])),
    pos = map_dbl(vader_output, ~ as.numeric(.x["pos"])),
    neu = map_dbl(vader_output, ~ as.numeric(.x["neu"])),
    neg = map_dbl(vader_output, ~ as.numeric(.x["neg"])),
    but_count = map_dbl(vader_output, ~ as.numeric(.x["but_count"]))
  )
```

```{r save-sentiment-vader-backend}
#| eval: false
qs::qsave(chats_vader, file = here("local_data/chats-vader.qs"))
```

```{r vader-data-overview}
chats_vader %>% 
    select(message_id, compound:but_count) %>% 
    head(n = 20)
```

### Zusammenführung Dictionary-Sentiments

```{r chats-sentiment-create}
#| eval: false
chats_sentiment <- chats %>% 
    left_join(chats_polarity, by = join_by("message_id" == "doc_id")) %>%
    left_join(chats_valence, by = join_by("message_id" == "doc_id")) %>% 
    left_join(chats_vader %>% 
        select(message_id, vader_output, word_scores, compound, pos, neu, neg, but_count), 
        by = "message_id")
```

```{r chats-sentiment-distribution}
chats_sentiment %>% 
    select(message_id, polarity, valence, compound) %>%
    datawizard::describe_distribution()
```

### Verschiedene VADER-Visualisierungen

```{r chats-sentiment-vader-subsample}
chats_vader_sample <- chats_vader %>%
    filter(message_length < 100) %>%
    slice_sample(n = 10) 

```

```{r chats-sentiment-compound-scores}
chats_vader_sample %>%
    ggplot(aes(x = message_content, y = compound, fill = compound > 0)) +
        geom_bar(stat = "identity", width = 0.7) +
        scale_fill_manual(values = c("TRUE" = "blue", "FALSE" = "red"), labels = c("Positive", "Negative")) +
        labs(
            title = "Overall Compound Sentiment for Each Sentence",
            x = "Sentences",
            y = "Compound Sentiment",
            fill = "Sentiment") +
        coord_flip() +  # Flip for easier readability
        theme_minimal() +
        theme(
            axis.text.x = element_text(angle = 45, hjust = 1))  # Label wrapping and adjusting angle
```

```{r chats-sentiment-word-level-scores}

chats_vader_sample %>% 
    mutate(
        pos_pct = pos * 100,
        neu_pct = neu * 100,
        neg_pct = neg * 100) %>% 
  select(message_content, pos_pct, neu_pct, neg_pct) %>% 
  pivot_longer(
    cols = c(pos_pct, neu_pct, neg_pct),
    names_to = "sentiment",
    values_to = "percentage") %>% 
  mutate(
    sentiment = factor(
        sentiment,
        levels = c("pos_pct", "neu_pct", "neg_pct"),
        labels = c("Positive", "Neutral", "Negative"))) %>% 
  ggplot(aes(x = message_content, y = percentage, fill = sentiment)) +
    geom_bar(stat = "identity", width = 0.7) +
    scale_fill_manual(values = c("Positive" = "blue", "Neutral" = "gray", "Negative" = "red")) +
    labs(
        title = "Proportion of Positive, Neutral, and Negative Sentiment",
        x = "Sentences",
        y = "Percentage",
        fill = "Sentiment") +
  coord_flip() +
  theme_minimal()
```

### Chat mit LLMs in R

#### ellmer

```{r ellmer-demo-1-llama3}
ellmer_chat_llama <- ellmer::chat_ollama(
    model = "llama3.2"
)

ellmer_chat_llama$chat("Why is the sky blue?")
```

```{r ellmer-demo-1-mistral}
ellmer_chat_mistral <- ellmer::chat_ollama(
    model = "mistral"
)

ellmer_chat_mistral$chat("Why is the sky blue?")
```

#### rollama

```{r ollama-demo-2-llama3_2}
demo_2_llama3_2 <- rollama::query(
     "What is the longest five letter word in english?",
    model = "llama3.2",
    screen = FALSE,
    output = "text"
)

glue::glue(demo_2_llama3_2)
```

```{r ollama-demo-2-mistral}
demo_2_mistral <- rollama::query(
    "What is the longest five letter word in english?",
    model = "mistral",
    screen = FALSE,
    output = "text"
)

glue::glue(demo_2_mistral)
```

```{r ollama-demo-3-llama3}
demo_3_llama3_2 <- rollama::query(
    "Is 9677 a prime number?",
    model = "llama3.2",
    screen = FALSE,
    output = "text"
)

glue::glue(demo_3_llama3_2)
```

```{r ollama-demo-3-mistral}
demo_3_mistral <- rollama::query(
    "Is 9677 a prime number?",
    model = "mistral",
    screen = FALSE,
    output = "text"
)

glue::glue(demo_3_mistral)
```

### Sentimentscores mit LLM

```{r rollama-sentiment-score-estimation}
# Erstellung einer kleinen Stichprobe
subsample <- chats_sentiment %>% 
    filter(message_length > 20 & message_length < 50) %>%
    slice_sample(n = 10) 

# Process each review using make_query
queries <- rollama::make_query(
    text = subsample$message_content,
    prompt = "Classify the sentiment of the provided text. Provide a sentiment score ranging from -1 (very negative) to 1 (very positive).",
    template = "{prefix}{text}\n{prompt}",
    system = "Classify the sentiment of this text. Respond with only a numerical sentiment score.",
    prefix = "Text: "
)

# Create sentiment score for different models
models <- c("llama3.2", "gemma2", "mistral")
names <- c("llama", "gemma", "mistral")
for (i in seq_along(models)) {
  subsample[[names[i]]] <- rollama::query(queries, model = models[i], screen = FALSE, output = "text")
}
```

```{r rollama-sentiment-score-comparison}
subsample %>% 
  select(message_content, polarity, valence, compound, llama, gemma, mistral) %>% 
  gt() 
```

### Weiteführende Analysen

```{r chats-sentiemnt-density-by-streamer}
chats_sentiment %>% 
    ggpubr::ggdensity(
        x = "compound",
        color = "streamer"
    )
```

```{r chats-sentiment-violin-plot}
#| code-fold: true
#| code-summary: "Expand for full code"

chats_sentiment %>% 
    mutate(message_length_fct = case_when( 
        message_length <= 7 ~ "<= 7 words",
        message_length > 7 & message_length <= 34 ~ "8 to 34 words",
        message_length >= 34 ~ "> 34 words")
     ) %>%
    group_by(message_length_fct) %>%
    mutate(n = n()) %>%
    ggviolin(
        x = "message_length_fct",
        y = "compound", 
        fill = "message_length_fct"
    ) +
    stat_summary(
        fun.data = function(x) data.frame(y = max(x) + 0.15, label = paste0("n=", length(x))),
        geom = "text",
        size = 3,
        color = "black"
    ) +
    labs(
        x = "Länge der Nachricht"
    )
```

### Beispiele für Validierung

```{r chats-sentiment-positive-messages-validation}
chats_sentiment %>% 
    filter(compound >= 0.95) %>% 
    arrange(desc(compound)) %>% 
    select(message_content, compound) %>% 
    head(n = 3) %>% 
    gt() %>% gtExtras::gt_theme_538()
```

```{r chats-sentiment-negative-messages-validation}
chats_sentiment %>% 
    filter(compound <= -0.95) %>% 
    arrange(compound) %>% 
    select(message_content, compound) %>% 
    head(n = 3) %>% 
    gt() %>% gtExtras::gt_theme_538()
```

```{r chats-sentiment-negative-messages-users}
chats_sentiment %>% 
    filter(compound >= 0.95) %>% 
    sjmisc::frq(
        user_name, 
        min.frq = 5,
        sort.frq = "desc")
```

## Exkurs: Machine Learning

::: callout-important
## Important information

-   The following code chunks were not part of the session or the slides.
-   Based on the **blog post (with screencast)** by [Julia Silge](https://juliasilge.com/blog/animal-crossing/), the following sections exemplify the implementation of sentiment analysis using the `tidymodels` package.
:::

### Extract data

```{r tidymodels-create-datat}
chats_tidymodels <- chats_sentiment %>% 
    mutate(
        rating = case_when(
            compound > 0.5 ~ "positive",
            compound < -0.5 ~ "negative",
            TRUE ~ "neutral"), 
        word_count = str_count(message_content, "\\S+")
    ) %>% 
    filter(rating != "neutral")
```

```{r tidymodels-overview-descriptives}
# Distribution of compound sentiment scores
chats_tidymodels %>% 
    ggplot(aes(x = compound)) +
        geom_histogram(binwidth = 0.1, fill = "lightblue", color = "darkblue") +
        labs(
            title = "Distribution of Compound Sentiment Scores",
            x = "Compound Sentiment",
            y = "Frequency") +
    theme_minimal()   

# Distribution of word count
chats_tidymodels %>% 
    ggplot(aes(word_count)) +
    geom_histogram(fill = "midnightblue", alpha = 0.8) +
    theme_minimal()

chats_tidymodels %>% 
    datawizard::describe_distribution(word_count)
```

### Build model

```{r tidymodels-split-data}
library(tidymodels)

set.seed(42)
chats_rating_splits <- initial_split(chats_tidymodels, strata = rating)
chats_ratings_train <- training(chats_rating_splits)
chats_ratings_test <- testing(chats_rating_splits)
```

```{r tidymodels-recipes}
library(textrecipes)

chats_ratings_rec <- recipe(rating ~ message_content, data = chats_ratings_train) %>% 
    step_tokenize(message_content) %>% 
    step_stopwords(message_content) %>%
    step_tokenfilter(message_content, max_tokens = 1000) %>%
    step_tfidf(message_content) %>% 
    step_normalize(all_predictors()) 

chats_ratings_prep <- prep(chats_ratings_rec)
```


```{r tidymodels-lasso-model}
lasso_spec <- logistic_reg(penalty = tune(), mixture = 1) %>%
  set_engine("glmnet")

lasso_wf <- workflow() %>%
  add_recipe(chats_ratings_rec) %>%
  add_model(lasso_spec)

lasso_wf
```

### Tune model parameters 

```{r tidymodels-bootstrap} 
lambda_grid <- grid_regular(penalty(), levels = 40)

set.seed(42)
chats_ratings_folds <- bootstraps(chats_ratings_train, strata = rating)
chats_ratings_folds
```

```{r tidymodels-tune-model}
#| eval: false
doParallel::registerDoParallel()

set.seed(2020)
lasso_grid <- tune_grid( 
  lasso_wf,
  resamples = chats_ratings_folds,
  grid = lambda_grid,
  metrics = metric_set(roc_auc, ppv, npv)
)
```

```{r tidymodels-save-lasso-grid-backend}
#| eval: false
#| echo: false
qs::qsave(lasso_grid, file = here("local_data/tidymodels-lasso_grid.qs"))
```


```{r tidymodels-collect-metrics-lasso-grid}
lasso_grid %>%
  collect_metrics()
```

```{r tidymodels-plot-metrics-lasso-grid}
lasso_grid %>%
  collect_metrics() %>%
  ggplot(aes(penalty, mean, color = .metric)) +
  geom_line(linewidth = 1.5, show.legend = FALSE) +
  facet_wrap(~.metric) +
  scale_x_log10()
```

### Choose the final model 

```{r tidymodels-select-best-lasso}
best_auc <- lasso_grid %>% select_best(metric = "roc_auc")
best_auc
```

```{r tidymodels-finalize-lasso}
final_lasso <- finalize_workflow(lasso_wf, best_auc)
final_lasso
```

```{r tidymodels-final-lasso-variable-importance}
library(vip)

final_lasso %>%
  fit(chats_ratings_train) %>%
  extract_fit_parsnip() %>%
  vi(lambda = best_auc$penalty) %>%
  group_by(Sign) %>%
  top_n(20, wt = abs(Importance)) %>%
  ungroup() %>%
  mutate(
    Importance = abs(Importance),
    Variable = str_remove(Variable, "tfidf_message_content_"),
    Variable = fct_reorder(Variable, Importance)
  ) %>%
  ggplot(aes(x = Importance, y = Variable, fill = Sign)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~Sign, scales = "free_y") +
  labs(y = NULL)
```

```{r tidymodels-final-lasso}
chats_ratings_final <- last_fit(final_lasso, chats_rating_splits)
chats_ratings_final %>%
  collect_metrics()
```

```{r tidymodels-confusion-matrix}
chats_ratings_final %>% 
  collect_predictions() %>%
  conf_mat(rating, .pred_class)
```
